\appendixchapter{Additional Requirements}
\label{apx:ch:extended-analysis}

\appendixsection{Use-cases for Validation}\label{apx:sec:use-cases}

Use cases:

\begin{enumerate}
    \item Configure Seating Arrangement:
    \begin{itemize}
        \item The cinema owner creates and configures seating arrangements for two cinema halls.
        \item The owner assigns seats to rows and categorizes them into \enquote{stalls}, \enquote{box}, or \enquote{box with service}.
        \item Once the seating configuration is complete, the hall is released for ticket sales.
    \end{itemize}
    
    \item Manage Film Library:
    \begin{itemize}
        \item The cinema owner can add, edit, or remove films from the cinema's film library.
    \end{itemize}
    
    \item Schedule Film Screenings:
    \begin{itemize}
        \item The cinema owner schedules film screenings and assigns them to available cinema halls.
        \item Each film can have multiple screenings in different halls.".
        \item Once the seating configuration is complete, the hall is released for ticket sales.
    \end{itemize}
    
    \item Customer Account Management:
    \begin{itemize}
        \item Customers can create or edit their accounts, which store their contact information and booking history.
    \end{itemize}
    
    \item Reserve Tickets:
    \begin{itemize}
        \item A customer chooses a screening and a desired seat category for which they want to reserve tickets.
        \item Customers can view real-time seat availability for a specific screening before making a reservation or booking.
        \item The system checks seat availability and allows reservations only if there are available seats.
        \item A customer can cancel their reservation.
        \item A customer can upgrade their reservation into a booking.
        \item The booking can not be canceled.
    \end{itemize}
    
    \item Direct Booking:
    \begin{itemize}
        \item A customer can directly book a ticket without a previous reservation.
    \end{itemize}
    
    \item Mark Screening as \enquote{Taken Place}:
    \begin{itemize}
        \item The cinema owner can mark a screening as "taken place" to prevent further bookings.
        \item Customers are now unable to book or reserve tickets for this screening.
    \end{itemize}
    
    \item Calculate Revenue:
    \begin{itemize}
        \item The cinema owner can view the revenue generated from a single screening or a single film based on the current bookings made.
        \item Reservations must not affect the calculation.
    \end{itemize}
    
    \item Client-Server Communication:
    \begin{itemize}
        \item Multiple client computers can be used to operate the cinema management software.
        \item The software ensures that messages from clients to the server are transmitted and unintended effects are avoided.
        \item Multiple clients booking or reserving the same ticket concurrently results in only a single client succeeding.
        \item The other clients are notified that their operation did not succeed.
    \end{itemize}
    
    \item Update Seating Arrangement:
    \begin{itemize}
        \item The cinema owner can update the seating arrangement in a cinema hall by modifying seat categories or deleting and adding rows and seats.
    \end{itemize}
    
    \item Edit Film Screening Details:
    \begin{itemize}
        \item The cinema owner can edit film screening details, such as the display name.
    \end{itemize}

\end{enumerate}

\appendixsection{Data Model Requirements}\label{apx:sec:model-requirements}

\renewcommand{\arraystretch}{1.25}
\begin{table}[H]
    \centering
    \caption{Summary of model requirements for \gls{g:cms}.}
    \label{apx:tab:model-requirements}
    \begin{tabular}{l|p{0.75\textwidth}}
        \toprule
        Model Requirement & Description \\ \midrule
        \modelrequirementdefshort\label{req-mdl:cinema} & Cinema management system is required \\ \hline
        \modelrequirementdefshort\label{req-mdl:Sale system} & Online ticket sale system \\ \hline
        \modelrequirementdefshort\label{req-mdl:hall} & Administration cinema halls (with seatrows, seats) \\ \hline
        \modelrequirementdefshort\label{req-mdl:screening} & Administration of movie screenings \\ \hline
        \modelrequirementdefshort\label{req-mdl:seatrow} &  Creation of any number of seatrows in a cinema hall\\ \hline
        \modelrequirementdefshort\label{req-mdl:seat} & Creation of any number of seats in a seatrow \\ \hline
        \modelrequirementdefshort\label{req-mdl:price category} & A seatrow needs a Price category \\ \hline
        \modelrequirementdefshort\label{req-mdl:sale release} & When the seating is complete, the cinema hall can be released for sale (reservations or bookings can be transacted) \\ \hline
        \modelrequirementdefshort\label{req-mdl:ScreeningAndHall} & A film screening has exactly one cinema hall \\ \hline
        \modelrequirementdefshort\label{req-mdl:FilmScreenings} & A film can be shown in several screenings (and halls)  \\ \hline
        \modelrequirementdefshort\label{req-mdl:Tickets} & Customer can book tickets for each movie screening, if the seat is free \\ \hline
        \modelrequirementdefshort\label{req-mdl:Reservation} & Reservation of a seat is only possible if the seat is free \\ \hline
        \modelrequirementdefshort\label{req-mdl:Cancel} & Reservation can be canceled \\ \hline
        \modelrequirementdefshort\label{req-mdl:ReservationToBooking} & The customer can modify the reservation into a booking \\ \hline
        \modelrequirementdefshort\label{req-mdl:Booking} & The customer can take a booking, he can no longer cancel it \\ \hline
        \modelrequirementdefshort\label{req-mdl:ScreeningFinished} & No timing component, but movie screening will be marked when it is over \\ \hline
        \modelrequirementdefshort\label{req-mdl:Revenues} & Cinema owner can view the complete revenues and the revenues of a single movie \\
        \bottomrule
    \end{tabular}
\end{table}
\renewcommand{\arraystretch}{1}