\chapter{Abstract}

As digitalization progresses, more and more industries require software solutions that can be adapted to their specific needs. In the area of cinema management, such an approach is necessary, as individual cinemas vary greatly in their size, equipment, and business model. This paper presents the development of a cross-platform network-based \glsfull{a:cms} prototype powered by C\# and Java. The \gls{g:cms} prototype addresses the unique requirements of cinema management, enabling users on any platform to register and manage their accounts, reserve and book movie tickets, and cancel previously retained reservations as needed. Cinema owners can effortlessly add new movies, schedule additional movie screenings, and manage their physical cinema infrastructure.

\vspace{.1cm}
\hspace{-.6cm}This work highlights the use of \glslong{a:mdd} techniques, leveraging the power of automated code generation with JetBrains \glsfull{a:mps} for the server-side data access layer to instead focus development ressources on providing an intuitive and user-friendly client application. Challenges encountered during development, such as the absence of native database transactions in the generated code, are discussed alongside the solutions implemented, such as a custom isolation layer. 

\vspace{.1cm}
\hspace{-.6cm}Although the final \gls{g:cms} prototype proves to be a reliable and viable software solution for cinema management, further work is required before deployment to production. This project contributes to the understanding of adapting software solutions to industry-specific requirements and demonstrates the potential of \glslong{a:mdd} in the cinema management domain.